Study of the hadronization of charged pions

### 2017-01-12 1-Answers-Review.tex

23.
P34, why do you have a 1\% normalization error in all the multiplicity ratios when you say just 
above that for this particular sample with two particles in the final state the events in the test 
regions dropped to 0.01?  Doesn’t that mean the target contamination normalization error is 
smaller than 1\%?

{\it Multiplicity ratios are a double ratio. The claim is that the semi inclusive part 
is not affected, but the inclusive electron ratio is affected. This is included
as a normalisation error. We revisited slightly the paragraph to make it clearer.} \\

24.
P34, with this technique of comparing results using the two different sets of variables (you 
call it two binnings, but I think that is sort of misleading), you are using the same events.  
Does this not mean you have a statistical contribution to this systematic error?  You say you 
noticed larger systematic errors for the pi- events due to lower acceptance and bigger 
weights.  Might it also be lower statistics and so you have statistical fluctuations contributing 
to the systematic error?  If so, you are sort of double-counting the statistical error and 
inflating the systematic error more than it should be.

{\it This is an interesting question and we might have overlooked this problem. WE
NEED TO THINK ABOUT THAT. } \\

@@

25.
P35 - It would clarify the discussion with a summary or table of the point-to-point systematic 
errors.

{\it The point-to-point errors include only contributions from the bad particle 
identifications and acceptance effects. It is also different for every bin, so
we did not think a table would be useful to summarize only two contributions.} \\

@@

26.
P35 -
 add plots with systematic uncertainty bands on it to demonstrate bin-by-bin values.

{\it FIGURES NEED TO BE UPDATED WITH NEW ERROR BAR DISPLAY.} \\

@@

27.
P35, end of top paragraph, you say you don’t include the acceptance systematic, but it looks 
to me like it is included in Table 8?  What am I missing?

{\it We decided to keep the normalization error, not the point to point. This was not
said clearly in the text, it is now clarified. TO CLARIFY WHEN SORTED OUT.} \\

@@

28.
P36, top paragraph, “that a factorization holds” means what??  Should explain.

{\it This sentence has been reformulated with an additional reference.} \\

@@

29.
P36 top of section 3.1.1, 5\% versus 5\% looks more like 1 sigma rather than the 1.5 sigma 
you say in the text.

{\it The reson we quote 1.5, is that one need to move $\pi^+$ one sigma down and $\pi^-$ one
sigma up. So for the overall normal deviation (sigma) we quadratically sum them,
leading to 1.5.} \\

@@

30.
P36, second paragraph of section 3.1.1, “... might be modified if the production time occurs 
inside the nucleus.”  I think I know what you mean but the language makes no sense.  You 
mean if the formation takes place inside the nucleus, right?

{\it This langage refers to figure 1, where we define a production time and a 
formation time. We tried to rephrase for more clarity.}\\

@@

31.
P42, top, “... that is seen in our result.”  Where do I see what you are discussing in the top 
two lines of this page.  I could not find whatever it is.  What should I be looking at?

{\it The phrasing was incorrect, hopefully the new version is better. We will work with 
the authors of the models to add some projections to our figures. This should eventually
make all these physics comments much clearer.} \\

### 2017-01-12 chap5.tex
Continue review questions, start English corrections

As the two married experiments aimed at comparing deuterium with heavy nuclei, it was decided to use a double target system~\cite{Hakobyan:2008zz}. The first target was filled with a liquid deuterium, and the second was a solid target. The latter was made of either carbon, aluminum, iron, tin or lead, and was changed remotely (see figure~\ref{fig:phototarget}). The two targets were separated by only 4~cm in order to minimize the difference on CLAS acceptance between them. The advantage of having two targets mounted simultaneously on the beam line is that several systematic effects related to the beam and detector's properties will cancel in the nuclear ratio.

@@

The analysis of the experiment E-02-110, focusing on the study of color 
transparency effects, has been approved and published~\cite{ElFassi:2008}. As this 
analysis went through a careful review by the CLAS collaboration, we have adapted similar analysis methods as much as possible. In particular, the electron selection 
presented here is very similar to theirs; the main difference being a new 
target determination method. The pion identification cuts are, however, tightened
in this analysis as we have less constraints on the kinematics to exclude any possible pions' contamination.

In the section \ref{sec:pid}, we identify the following particles, e$^-$, 
$\pi^-$ and $\pi^+$ using a series of cuts on various detector outputs. For pions, we require a positive status of drift chambers (DC) and scintillator counters (SC) local signals, in addition to the global status reconstructed with the time-based tracking correction. For electron identification, we use good signals from 
all detectors, DC, Cherenkov Counters (CC), SC and the Electromagnetic 
Calorimeter (EC).

Once all particles are identified, we extract our two observables, multiplicity 
ratios and the transverse momentum broadening. Their derivation method is presented in the section \ref{sec:obs}, while a list of our corrections is summarized in the section \ref{sec:corrections}. The budget of our systematical uncertainties is detailed in the section \ref{sec:TotSys}, and the final analysis results are presented and discussed in the next chapter.

@@

where $\mu = 0.271$ is the mean of the total energy fraction deposited in the 
calorimeter, the parameter $a$ is set to 0.5, and the parameter 
$b$ varies with momenta, as shown in table \ref{tab:ecoutin-par}. The derivation of $b$ was motivated by the non-linear momentum dependence of the energy 
deposited on both EC regions (see figure \ref{eleEC}). As pions are 
minimum ionizing particles, they are expected to loose a constant energy in 
the inner part of the calorimeter (around 30~MeV), regardless of their 
momenta. Therefore, by requesting more than 60~MeV to be deposited, we 
efficiently cut the pion contamination (see figure~\ref{eleECi}).

@@

After testing several different acceptance correction methods, we finally converged with the one using the two different binning presented on a table \ref{tab:AcceptBinning}. The difference between these methods gave us an idea about the systematic error associated with this correction. Using our results on iron, we found the relative uncertainties presented in a table~\ref{tab:SysAcc}. We noticed the significantly large errors for $\pi^-$s, which were expected, due to their low acceptance and larger weights. Although, systematical errors are considerably large on \dpt measurements. This is mainly due to the nature of the \dpt observable; as a difference, it would indeed enhance relative errors significantly. As it was shown in figure~\ref{fig:AcceptPlots}, error bars became much larger for the corrected \dpt from the acceptance effect. This fact indicated an important statistical sensitivity introduced by our weighting methods. The errors on \dpt are of the same order, or smaller, than the differences observed between the two weighted data-sets. This is an indication that the uncertainties reported in table \ref{tab:SysAcc} are, in nature, similar to the statistical errors, in the sense that both originate from the large variation between event-by-event weights. For this reason, we decided to do not include this error in our systematic budget to avoid double counting this effect.

@@

The point-to-point errors include contributions from a detection contamination and acceptance effects. However, the normalization errors, which are independent of kinematical variables and due to acceptance effects, a target's misidentification and the isospin correction, are summarized in a table~\ref{tab:sysid}.

>>>>

As the two experiments aimed at comparing deuterium with heavy nuclei, it was 
decided to use a double target system~\cite{Hakobyan:2008zz}. The first target 
was filled with liquid deuterium, and the second was a solid target. The 
latter was made of either carbon, aluminum, iron, tin or lead, and was changed 
remotely (see figure~\ref{fig:phototarget}). The two targets were separated by 
only 4~cm in order to minimize the difference on CLAS acceptance between them. 
The advantage of having two targets mounted simultaneously on the beam line is 
that several systematic effects related to the beam and detector properties 
cancel in the nuclear ratio.

@@

The analysis of the experiment E-02-110, focusing on the study of color 
transparency effects, has been approved and published~\cite{ElFassi:2008}. As this 
analysis went through a careful review by the CLAS collaboration, we have adapted similar analysis methods as much as possible. In particular, the electron selection 
presented here is very similar to theirs; the main difference being a new 
target determination method. The pion identification cuts are, however, tightened
in this analysis as we have less constraints on the kinematics to exclude any possible pion contamination.

In the section \ref{sec:pid}, we identify the following particles, e$^-$, 
$\pi^-$ and $\pi^+$ using a series of cuts on various detector outputs. For pions, we require a signal in the drift chambers (DC) and scintillator counters (SC) in 
addition to the successful reconstruction of the time-based tracking. For electron 
identification, we use the same standards but requesting a good signal from 
all detectors, DC, Cherenkov Counters (CC), SC and Electromagnetic 
Calorimeter (EC).

Once all particles are identified, we extract our two observables, 
multiplicity ratios and the transverse momentum broadening. The derivation 
of these quantities is presented in section \ref{sec:obs}, while a list of 
corrections  is summarized in section \ref{sec:corrections}. The systematic 
uncertainty budget is detailed in section \ref{sec:TotSys}, and the final 
analysis results are presented and discussed in the next chapter.

@@

where $\mu = 0.271$ is the mean of the total energy fraction deposited in the 
calorimeter, the parameter $a$ is set to 0.5 and the parameter 
$b$ varies with momentum, as shown in table \ref{tab:ecoutin-par}. The derivation of $b$ was motivated by the non-linear momentum dependence of the energy 
deposited on both EC regions (see figure \ref{eleEC}). As pions are 
minimum ionizing particles, they are expected to loose a constant energy in 
the inner part of the calorimeter (around 30~MeV), regardless of their 
momenta. Therefore, by requesting more than 60~MeV to be deposited, we 
efficiently cut the pion contamination (see figure~\ref{eleECi}).

@@

After testing several different acceptance correction methods, we finally 
converged with the one using four dimensions and a limited number of bins.
The two different approaches to binning the data presented on a table 
\ref{tab:AcceptBinning} are used to evaluate the systematic errors. The 
difference between these two methods on iron data are used to evaluate 
the relative uncertainties presented in a table~\ref{tab:SysAcc}. We noticed 
the significantly large errors for $\pi^-$s, which were expected, due to their 
lower acceptance and larger weights.

Systematic errors are also
considerably larger for \dpt measurements. This is mainly due to the nature of 
the \dpt observable; as it is a difference, it enhances relative errors 
significantly. Also, as shown in figure~\ref{fig:AcceptPlots}, error bars 
became much larger for the corrected \dpt from the acceptance effect. This 
result indicated an important statistical sensitivity introduced by our 
weighting methods. The errors on \dpt are of the same order, or smaller, than 
the differences observed between the two weighted data-sets. This is an 
indication that the uncertainties reported in table \ref{tab:SysAcc} are, in 
nature, similar to the statistical errors, in the sense that both originate 
from the large variation between event-by-event weights. For this reason, we 
decided not to include this error in our systematic budget to avoid double 
counting this effect.

@@

The point-to-point errors include contributions from the bad particle 
identifications and acceptance effects. The normalization error, which is 
independent of kinematic variables, are due to acceptance effects, target 
misidentification and isospin correction; the constributions are summarized 
in table~\ref{tab:sysid}.

### 2017-01-12 chap6.tex
Continue review questions, start English corrections

The results presented in this chapter are a selection of the observables 
that we want to use in the first publication, eventually a long paper will
include results as function of all variables. All results were extracted with the following DIS selection cuts: 
$Q^2$~$>$~$1$~GeV$^2$/c$^2$, $W$~$>$~$2$ GeV and $y<0.85$. To ensure that a factorization holds, we are selecting events with $0.4$~$<$~$z$~$<$~$0.7$~\footnote{This cut is not applied for plots with results as a function of $z$.} based on the previously published results from \cite{Asaturyan:2011mq}. Moreover, this cut also ensures that we are measuring the leading hadron, and avoiding the high $z$ region, which might be contaminated by 
the decay products of the diffractive production of $\rho^0$. Finally, we are applying a cut on $x_F > 0$ to select the forward fragmentation region.

@@

The attenuation, presented in the figure \ref{fig:RA}, is not linear neither for $A^{1/3}$ nor $A^{2/3}$. The HERMES data have already showed some indication 
of this feature~\cite{Airapetian:2007vu,Airapetian:2009jy}, but here, the non-linearity, which has important implication on models, is clear. Indeed, it seems difficult to conciliate the prehadron absorption models with this result. Prehadrons 
are expected to have their cross sections increasing with time and, therefore, 
distance. On the parton energy loss side, the BDMPS calculation gives a parton energy loss proportional to $L^2 \propto A^{2/3}$, which is in contradiction with this result. However, this statement does not hold at low energy, and might be 
modified if the production time occurs inside the nuclei.

@@

The $A$ dependence of the transverse momentum broadening, presented in 
figure~\ref{fig:PA}, is a crucial result. The combination of our large statistics with a wide $A$ coverage gave an outright indication of $A^{1/3}$ dependence of \dpt. This \dptp~ effect is found much smaller compared to HERMES measurment\cite{Airapetian:2009jy}, which is consistent with theoretical models predicting larger effects at larger energies. However, calculations of the parton energy loss from BDMPS \cite{Baier:1996sk} correlated \pt with the nuclei radii. A feature that is not enhanced in our result. Although, by looking to the low energy of our CLAS experiment, one might argue the validity of a direct comparison with BDMPS calculations. Nonetheless, this result shows an unexpected pattern that remains to be explained. One interpretation might favor the occurrence of the production time inside nuclei, as we proposed for the $A^{1/3}$ dependence of multiplicity ratios. In this case, the colored parton would not interact with the whole nuclei which limit the nuclear effect.

@@

Finally, the $Q^2$ dependence of \dpt is an important result for the BDMPS based 
calculation from \cite{Domdey:2008aq}. They have expected a raise of \dpt with $Q^2$, which is not observed in a figure \ref{fig:PQ2}. Even a tighter $\nu$ bin and a carbon normalization (see figure \ref{fig:PQ2-detailed}) gave a similar result. In conclusion, within error bars, no effect is observed for \dpt as a function of $Q^2$. However, as a theoretical input is missing, it is not clear if we have the needed resolution to observe the effect expected within BDMPS based models.

>>>>

The results presented in this chapter are a selection of the observables 
that we want to use in the first publication, eventually a long paper will
include results as function of all variables. All results were extracted with the following DIS selection cuts: 
$Q^2$~$>$~$1$~GeV$^2$/c$^2$, $W$~$>$~$2$ GeV and $y<0.85$. To ensure that SIDIS 
factorization applies~\cite{Mulders:2000jt}, we are selecting events with 
$0.4$~$<$~$z$~$<$~$0.7$~\footnote{This cut is not applied for plots with results 
as a function of $z$.} based on the previously published results from 
\cite{Asaturyan:2011mq}. Moreover, this cut also ensures that we are measuring the 
leading hadron, and avoiding the high $z$ region, which might be contaminated by 
the decay products of the diffractive production of $\rho^0$. Finally, we are 
applying a cut on $x_F > 0$ to select the forward fragmentation region.

@@

The attenuation, presented in the figure \ref{fig:RA}, is neither linear as a 
function of $A^{1/3}$ nor as a function of $A^{2/3}$. The HERMES data had
already showed some indication 
of this feature~\cite{Airapetian:2007vu,Airapetian:2009jy}, but here the 
non-linearity, which has important implication on models, is clear. Indeed, 
it seems difficult to conciliate the prehadron absorption models with this result. Prehadrons 
are expected to have their cross sections increasing with time and, therefore, 
distance. On the parton energy loss side, the BDMPS calculation gives a parton 
energy loss proportional to $L^2 \propto A^{2/3}$, indicating that we are not
in the region where this result applies. Morover, if the production 
time\footnote{As defined in figure~\ref{fig:hadro}} occurs 
inside the nuclei, the behavior of the multiplicity ratio can be more complicated
as different processes intervene.

@@

The $A$ dependence of the transverse momentum broadening, presented in 
figure~\ref{fig:PA}, is a crucial result. The combination of our large 
statistics with a wide $A$ coverage gave an outright indication of $A^{1/3}$ 
dependence of \dpt. This \dptp~ effect is found much smaller compared to 
HERMES measurment\cite{Airapetian:2009jy}, which is consistent with
 theoretical models predicting larger effects at larger energies. However, 
calculations of the parton energy loss from BDMPS \cite{Baier:1996sk} 
correlated \pt with quadratically the nuclei radii. A feature that is not 
observed in our result. Although, by looking to the low energy of our CLAS 
experiment, one might argue the validity of a direct comparison with BDMPS 
calculations. Nonetheless, this result shows an unexpected pattern that 
remains to be explained. One possible interpretation is the occurrence of 
the production time inside the nuclei, as we proposed for the $A^{1/3}$ 
dependence of multiplicity ratios. In this case, the colored parton would 
not interact with the whole nuclei, hence limiting the nuclear effect.

@@

Finally, the $Q^2$ dependence of \dpt is an important result for the BDMPS based 
calculation from \cite{Domdey:2008aq}. They have expected a raise of \dpt with $Q^2$, 
which is not observed in figure \ref{fig:PQ2}. Using a tighter $\nu$ bin and a 
carbon normalization should isolate this effect better, but figure \ref{fig:PQ2-detailed}
gives a similar result. In conclusion, within error bars, no effect is observed for 
\dpt as a function of $Q^2$. However, we would like to have a quantitative theoretical 
input here, as it is not clear if we have the needed resolution to observe the effect 
expected within BDMPS based models. We are going to work with the authors of the original 
paper to add some projections on our figures.

### 2017-01-12 intro.tex
Continue review questions, start English corrections

The hadronization in nuclear matter is a key process of the Quantum Chromo-Dynamics theory (QCD) because it leads to major theoretical uncertainties in numerous measurements. As the nuclear medium is hot and evolving in Relativistic Heavy Ion Collisions (RHIC), DIS experiments at JLab energies are well suited to test different theoretical models, including the RHIC's ones, because the size of cold nuclei is stable and known. The hadronization can give important information about nuclei through the quark energy loss, for example, Arleo's model~\cite{Arleo:2003yf} correlates the quark energy loss with a gluon density, and Kopeliovich et al.'s model~\cite{Kopeliovich:2010aa} correlates the $\Delta \langle P_T^2 \rangle$ with the saturation scale. Other models \cite{Gallmeister:2007an} utilize different assumptions to describe the pre-hadron evolution into a full hadron. Therefore, high precision measurements are very important to discriminate between different models.

@@

In order to best constrain the models with our data, we extracted our results using tight multi-dimensional binning. That is possible because of the high statistics of our EG2 data, which allowed the study of both pions production over a wide kinematic range.

@@

In \cite{Wang:2002ri}, E.~Wang and X.-N.~Wang, described HERMES data using only 
the parton energy loss, hence the observed suppression is due to the fact that a lower energy quark fragments into a low number of hadrons at a very low $z$. This kind of models is suitable for both RHIC and nDIS experiments since it permits a common interpretation of hadron suppression in the nuclear matter. Moreover, various calculations have described the parton energy loss in the nuclear medium using the $\hat q$ (GeV$^2$ fm$^{-1}$) parameter, that is defined as the quark transverse momentum normalized by its propagation path length. In these models, $\hat q$ is mainly related to the $P_T$ broadening observable. The main difficulty of quark energy loss models is the lack of a coherent description for both multiplicity ratios and $P_T$ broadening behaviors. Recent models used a $\hat q$ to reproduce multiplicity ratio, which is too large to describe the transverse momentum broadening.
% TODO Add a ref

@@

Hadron multiplicity ratios in nuclei were measured in numerous lepton 
facilities: L.S.~Osborne {\it et al.} \cite{Osborne:1978ai} at SLAC,
L.~Hand {\it et al.} \cite{Hand:1978tx}, the E665 collaboration \cite{Adams:1994ri} at FNAL, and the European Muon Collaboration \cite{Arvidson:1984fz,Ashman:1991cx} at CERN. These measurements revealed the main features of the hadronization mechanism
in nuclei by showing a suppression of hadrons' production in heavy nuclei.
This suppression appears to be reduced at higher $\nu$ and lower $z$, and it 
can even inverse sign and become an increased yield at very low $z$.

@@

The good precision of HERMES data shed light on new hadronization features, such as the behavior of K$^+$s, which have less attenuation than pions (see figure \ref{fig:her1}) but an excess on $\Delta \langle P_T^2 \rangle$. Must note that it is difficult to reproduce this behavior on models where only one hadronization stage is taken into account to explain all effects. Likewise, the different behavior of protons compared to anti-protons (see figure \ref{fig:her2}) is interesting and needs more precise analyses to unravel it since most of the existing models do not treat yet the baryons' hadronization.

>>>>

The hadronization in nuclear matter is a key process of the Quantum 
Chromo-Dynamics theory (QCD) because it leads to major theoretical 
uncertainties in numerous measurements. DIS experiments at JLab energies are 
well suited to test different theoretical models of hadronization, including 
the ones used for Relativistic Heavy Ion Collisions (RHIC). The main advantage 
of testing models in lepton scattering is that the size of cold nuclei is 
stable and known, while in RHIC the nuclear medium is hot and evolving 
introducing many parameters and unknowns. The hadronization process can also 
give important information about nuclei through the quark energy loss, for example, Arleo's model~\cite{Arleo:2003yf} correlates the quark energy loss with a gluon density, and Kopeliovich et al.'s model~\cite{Kopeliovich:2010aa} correlates the $\Delta \langle P_T^2 \rangle$ with the saturation scale. Other models \cite{Gallmeister:2007an} utilize different assumptions to describe the pre-hadron evolution into a full hadron. Therefore, high precision measurements are very important to discriminate between different models.

@@

In order to best constrain the models with our data, we extracted our results using tight multi-dimensional binning. That is possible because of the high statistics of our EG2 data, which allowed the study of both pion production on a wide kinematic range.

@@

In \cite{Wang:2002ri}, E.~Wang and X.-N.~Wang, described HERMES data using only 
the parton energy loss, hence the observed suppression is due to the fact that a lower energy quark fragments into a low number of hadrons at a very low $z$. This kind of model is suitable for both RHIC and nDIS experiments since it permits a common interpretation of hadron suppression in the nuclear matter. Moreover, various calculations have described the parton energy loss in the nuclear medium using the $\hat q$ (GeV$^2$ fm$^{-1}$) parameter, that is defined as the quark transverse momentum normalized by its propagation path length. In these models, $\hat q$ is mainly related to the $P_T$ broadening observable. The main difficulty of quark energy loss models is the lack of a coherent description for both multiplicity ratios and $P_T$ broadening behaviors. Recent models used a $\hat q$ to reproduce multiplicity ratio, which is too large to describe the transverse momentum broadening.
% TODO Add a ref

@@

Hadron multiplicity ratios in nuclei were measured in numerous lepton 
facilities: L.S.~Osborne {\it et al.} \cite{Osborne:1978ai} at SLAC,
L.~Hand {\it et al.} \cite{Hand:1978tx}, the E665 collaboration \cite{Adams:1994ri} at FNAL, and the European Muon Collaboration \cite{Arvidson:1984fz,Ashman:1991cx} at CERN. These measurements revealed the main features of the hadronization mechanism
in nuclei by showing a suppression of hadrons' production in heavy nuclei.
This suppression appears to be reduced at higher $\nu$ and lower $z$, at very 
low $z$ it can even change sign and become an increased yield.

@@

The good precision of HERMES data shed light on new hadronization features, 
such as the behavior of K$^+$s, which have less attenuation than pions (see 
figure \ref{fig:her1}) but an excess in $\Delta \langle P_T^2 \rangle$. It is 
notable that it is difficult to reproduce this behavior in models where only 
one hadronization stage is taken into account to explain all effects. Likewise, 
the different behavior of protons compared to anti-protons (see figure 
\ref{fig:her2}) is interesting but most existing models do not treat baryon 
hadronization yet.
